Lesson 3
========================================================

## Reading Data
```{r}


```

## Histogram of User's Birthdays
```{r}



```



***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
getwd
list.files()
pf <- read.csv('pseudo_facebook.tsv', sep = '\t')
names(pf)
```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
library(ggplot2)
names(pf)
qplot(x = dob_day, data = pf) + 
  scale_x_continuous(breaks = 1:31)

ggplot(aes(x = dob_day), data = pf) + 
  geom_histogram(binwidth = 1) + 
  scale_x_continuous(breaks = 1:31) + 
```

***

#### What are some things that you notice about this histogram?
Response:

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}
ggplot(aes(x = dob_day), data = pf) + 
  geom_histogram(binwidth = 1) + 
  scale_x_continuous(breaks = 1:31) + 
  facet_wrap(~dob_month, ncol = 3)
```

#### Let’s take another look at our plot. What stands out to you here?
Response:

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
library(ggplot2)
ggplot(aes(x = friend_count), data = pf)+
  geom_histogram()

```

#### How is this plot similar to Moira's first plot?
Response:

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
ggplot(aes(x = friend_count), data = pf, binwidth = 25)+
  geom_histogram()+
  scale_x_continuous(limits = c(0,1000), breaks = seq(0,1000,50))

```

### Exploring with Bin Width
Notes:

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
ggplot(aes(x = friend_count), data = subset(pf, !is.na(gender)), binwidth = 25)+
  geom_histogram()+
  scale_x_continuous(limits = c(0,1000), breaks = seq(0,1000,50))+
  facet_wrap(~gender)


qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}
ggplot(aes(x = friend_count), data = subset(pf, !is.na(gender)), binwidth = 25)+
  geom_histogram()+
  scale_x_continuous(limits = c(0,1000), breaks = seq(0,1000,50))+
  facet_wrap(~gender)
```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
table(pf$gender)
by(pf$friend_count, pf$gender, summary)
```

#### Who on average has more friends: men or women?
Response:

#### What's the difference between the median friend count for women and men?
Response:

#### Why would the median be a better measure than the mean?
Response:

***

### Tenure
Notes:

```{r Tenure}
ggplot(aes(x = tenure), data= pf)+
  geom_histogram(binwidth = 30, color = 'black', fill = '#099DD9')


```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
ggplot(aes(x = tenure/365), data= pf)+
  geom_histogram(binwidth = .25, color = 'black', fill = '#F79420')+
  scale_x_continuous(breaks = seq(1,7,1), limits = c(0,7))+
  xlab('Number of years using Facebook') + 
  ylab('Number of users in sample')

```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
ggplot(aes(x = tenure/365), data= pf)+
  geom_histogram(binwidth = .25, color = 'black', fill = '#F79420')+
  scale_x_continuous(breaks = seq(1,7,1), limits = c(0,7))+
  xlab('Number of years using Facebook') + 
  ylab('Number of users in sample')
```

***

### User Ages
Notes:

```{r User Ages}
library(ggplot2)
ggplot(aes(x = age), data = pf) + 
  geom_histogram(binwidth = 1, color = 'black', fill = '#F79420')+
  scale_x_continuous(breaks = seq(1,130,10))
  xlab('Age')+
  ylab('Number of users in sample')

```

#### What do you notice?
Response:

***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:

***

```{r}
ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram(binwidth = 100, color = 'black', fill = '#F79420')+
  xlab('Number of friends')+
  ylab('Number of users in sample')

summary(pf$friend_count)
summary(log10(pf$friend_count + 1))
summary(sqrt(pf$friend_count + 1))

# define individual plots
library(gridExtra)
p1 <- ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram(binwidth = 100, color = 'black', fill = '#F79420')+
  xlab('Number of friends')+
  ylab('Number of users in sample')
p2 <- p1+
  scale_x_log10()+
  xlab('Number of friends')+
  ylab('Number of users in sample')
p3 <- p1+
  scale_x_sqrt()+
  xlab('Number of friends')+
  ylab('Number of users in sample')
# arrange plots in grid
grid.arrange(p1, p2, p3, ncol=1)
```

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}
# define individual plots
library(gridExtra)
p1 <- ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram(binwidth = 100, color = 'black', fill = '#F79420')+
  xlab('Number of friends')+
  ylab('Number of users in sample')
p2 <- p1+
  scale_x_log10()+
  xlab('Number of friends')+
  ylab('Number of users in sample')
p3 <- p1+
  scale_x_sqrt()+
  xlab('Number of friends')+
  ylab('Number of users in sample')
# arrange plots in grid
grid.arrange(p1, p2, p3, ncol=1)
```

***



### Frequency Polygons

```{r Frequency Polygons}
summary(pf$www_likes)

ggplot(aes(x = www_likes, y = ..count../sum(..count..)), data = subset(pf, !is.na(gender))) +
  geom_freqpoly(aes(color = gender)) + 
  ##scale_x_continuous() + 
  scale_x_log10() +
  xlab('Likes') + 
  ylab('Percentage of users with that friend count')

```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
summary(pf)
pf_male <- subset(pf, gender == 'male')
pf_female <- subset(pf, gender == 'female')
sum(pf_male$www_likes)
sum(pf_female$www_likes)

by(pf$www_likes, pf$gender, sum)

```


***

### Box Plots
Notes:

```{r Box Plots}
library(ggplot2)
qplot(x = gender, y = friend_count,
       data = subset(pf, !is.na(gender)),
       geom = 'boxplot', ylim = c(0,1000))

qplot(x = gender, y = friend_count,
       data = subset(pf, !is.na(gender)),
       geom = 'boxplot') +
  scale_y_continuous(limits = c(0,1000))

qplot(x = gender, y = friend_count,
       data = subset(pf, !is.na(gender)),
       geom = 'boxplot') +
  coord_cartesian(ylim = c(0,1000))


```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}

qplot(x = gender, y = friend_count,
       data = subset(pf, !is.na(gender)),
       geom = 'boxplot') +
  coord_cartesian(ylim = c(0,1000))
```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}

by(pf$friend_count, pf$gender, summary)


```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}

by(pf$friendships_initiated, pf$gender, summary)


```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}

summary(pf$mobile_likes)

summary(pf$mobile_likes > 0)

pf$mobile_check_in <- NA
pf$mobile_check_in <- ifelse(pf$mobile_likes > 0, 1, 0)
pf$mobile_check_in <- factor(pf$mobile_check_in)
summary(pf$mobile_check_in)

mobile_check_in_0 <- subset(pf$mobile_check_in, pf$mobile_check_in == '0')
mobile_check_in_1 <- subset(pf$mobile_check_in, pf$mobile_check_in == '1')

percentage <- length(mobile_check_in_1) / (length(mobile_check_in_0) + length(mobile_check_in_1))


```

Response:

***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!