Lesson 5
========================================================
getwd()
#setwd('C:/Users/Tulio/Documents/Cursos/Udacity/Nanodegree_Data_Scientist/EDA_Course_Materials/lesson5')
setwd('C:/Users/tmg2/Desktop/Udacity/EDA_Course_Materials/lesson5')

pf <- read.csv('pseudo_facebook.tsv', sep = '\t')
### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes:

***

### Third Qualitative Variable
Notes:

```{r Third Qualitative Variable}
library(dplyr)
library(ggplot2)
ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + geom_boxplot()+
  stat_summary(fun.y = mean, geom = 'point', shape = 4)

ggplot(aes(x = age, y = friend_count),
       data = subset(pf, !is.na(gender))) +
  geom_line(aes(color = gender), stat = 'summary', fun.y = median)

pf.fc_by_age_gender <- subset(pf, !is.na(gender)) %>% 
  group_by(age, gender) %>% 
  summarise(mean_friend_count = mean(friend_count),
            median_friend_count = median(friend_count),
            n = n())

ggplot(aes(x = age, y = median_friend_count), data = pf.fc_by_age_gender) +
  geom_line(aes(color = gender))

```

***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}

```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***

### Reshaping Data
Notes:

```{r}
#install.packages('reshape2')
#install.packages('tidyr')
#library(reshape2)

library(tidyr)

pf.fc_by_age_gender.wide <- spread(select(pf.fc_by_age_gender, age, gender, median_friend_count), gender, median_friend_count)



```


***

### Ratio Plot
Notes:

```{r Ratio Plot}

?geom_hline
?linetype

pf.fc_by_age_gender.wide$ratio <- pf.fc_by_age_gender.wide$female / pf.fc_by_age_gender.wide$male

ggplot(aes(x = age, y = ratio), data = pf.fc_by_age_gender.wide) +
  geom_line()+
  geom_hline(yintercept = 1, linetype = 2)



```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}

pf$year_joined <- floor(2014 - (pf$tenure / 365))

```

***

### Cut a Variable
Notes:

```{r Cut a Variable}

pf$year_joined.bucket <- cut(pf$year_joined, breaks = c(2004, 2009, 2011, 2012, 2014))



```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}

table(pf$year_joined.bucket, useNA = 'ifany')

ggplot(aes(x = age, y = friend_count), 
       data = subset(pf, !is.na(gender)))+
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = median)

```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}

ggplot(aes(x = age, y = friend_count), 
       data = subset(pf, !is.na(gender)))+
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean)+
  geom_line(stat = 'summary', fun.y = mean, linetype = 2, color = 'Black')

ggplot(aes(x = age, y = friend_count), 
       data = subset(pf, !is.na(gender)))+
  geom_point(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean)+
  geom_line(stat = 'summary', fun.y = mean, linetype = 2, color = 'Black')

```

***

### Friending Rate
Notes:

```{r Friending Rate}



with(subset(pf, tenure >= 1), summary(friend_count/tenure))

```

***

### Friendships Initiated
Notes:

What is the median friend rate?

What is the maximum friend rate?

```{r Friendships Initiated}

ggplot(aes(x = tenure, y = friendships_initiated/tenure), 
       data = subset(pf, tenure >= 1))+
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = median)

```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}

yo <- read.csv('yogurt.csv')
str(yo)


yo$id <- factor(yo$id)
str(yo)

ggplot(aes(x = price), data = yo)+
  geom_histogram(binwidth = 10)

summary(yo)

length(unique(yo$price))
table(yo$price)

```

***

### Number of Purchases
Notes:

```{r Number of Purchases}

yo$all.purchases <- yo$strawberry + yo$blueberry + yo$pina.colada + yo$plain + yo$mixed.berry

yo <- transform(yo, all.purchases = strawberry + blueberry + pina.colada + plain + mixed.berry)

summary(yo$all.purchases)

```

***

### Prices over Time
Notes:

```{r Prices over Time}

ggplot(aes(x = all.purchases), data = yo)+
  geom_histogram(binwidth = 1)

ggplot(aes(x = time, y = price), data = yo)+
  geom_point(alpha = 1/10,
            position = position_jitter(h = 1))

```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}

set.seed(1888)
sample.ids <- sample(levels(yo$id), 16)

ggplot(aes(x = time, y = price),
       data = subset(yo, id %in% sample.ids))+
  facet_wrap(~id)+
  geom_line()+
  geom_point(aes(size = all.purchases), pch = 1)

```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:
```{r}
install.packages('GGally')
library(GGally)


theme_set(theme_minimal(20))

set.seed(1836)


pf_subset <- pf[,c(2:15)]
names(pf_subset)
ggpairs(pf_subset[sample.int(nrow(pf_subset), 1000),])

```


***

### Even More Variables
Notes:



***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}

library(reshape2)
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

